---
title: "Plotly Presentation Assignment"
author: "Nicolaas Kuit"
date: "June 19, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Plotly Presentation Assignment
The next slide will show a plot of price rankings of various TSX stocks compared to a large basket of stocks.  
We'll look at the rank of the following stocks:   

* VNP.TO  
* DC-A.TO  
* SMF.TO  
* LUC.TO  
* PG.TO  

## Stock Rankings over 6 days
```{r, echo=FALSE}
prices <- read.table("priceData", header = TRUE, stringsAsFactors = FALSE)
numStocks <- length(unique(prices$YahooSymbol))

plot_ly(data = filter(prices, YahooSymbol %in% c("VNP.TO", "DC-A.TO", "SMF.TO", "LUC.TO", "PG.TO")), 
             x = ~PriceDate, 
             y = ~(CloseRank * 100), 
             color=~YahooSymbol, 
             type="scatter", 
             mode="lines+markers", 
             hoverinfo="text", 
             text=~paste(round(CloseRank * 100, 2), "%: ", YahooSymbol, sep="")
             ) %>% 
    layout(title = paste("Stock price rankings relative to a basket of", numStocks, "stocks"),
           xaxis = list(title = "Date"),
           yaxis = list(title = "Price ranking in % terms"),
           hovermode='compare')
```

## What does the graph show us?
Over a six day period:  
- VNP.TO **increased** its price ranking the most.  
- PG.TO and LUC.TO **decreased** its price ranking the most.
